Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-04-20 cthpc-2017/paper.tex
Revise wording

The overall system architecture is shown in figure \ref{fig:overall_arch}.

@@

We limited the budget of whole hardware under 100 dollars USD, but the autonomous vehicle prototype still has abilities of lane following, multiple car Interaction and route planning. The table \ref{hardware_list} shows the details.

>>>>

The system is designed for multiple self-driving cars, enabling collaborative computer vision, map navigation, motor control, and wireless communications, shown in figure \ref{fig:overall_arch}. It aggregates local pose graphs obtained from its multiple cars into a global pose graph, which it then feeds back to the cars to increase their mapping and localization effectiveness.

@@

Despite limited the budget shown in table \ref{hardware_list}, our autonomous vehicle prototype still has abilities of lane following, multiple car Interaction and route planning.
